CF Registry Analysis

### 2024-11-12 Christine Chan/CF Registry/cf_registry_survival_analysis.qmd
saved nice figures

```{r results='asis'}
f_vx770 <- update(f, . ~ . + A_Vx770)
vx770_cox_res <- coxph(f_vx770,
  data = annual[annual$ReviewYear >= 2011, ],
  cluster = eDWID
)
vx770_cox_res %>%
  tbl_regression(exponentiate = T)
ggcoef_table(vx770_cox_res,
  show_p_values = F, add_reference_rows = T, exponentiate = T,
  signif_stars = F, colour = F
)
```

@@

```{r}
f_vx809comb <- update(f, . ~ . + A_VX809comb)
vx809comb_cox_res <- coxph(f_vx809comb,
  data = annual[annual$ReviewYear >= 2015, ],
  cluster = eDWID
)
vx809comb_cox_res %>%
  tbl_regression(exponentiate = T)
ggcoef_table(vx809comb_cox_res,
  show_p_values = F, add_reference_rows = T, exponentiate = T,
  signif_stars = F, colour = F
)
```

@@

```{r}
tbl_merge(
  tbls = list("2003 - 2008" = t1, "2009 - 2013" = t2, "2014 - 2018" = t3)
)
ggcoef_compare(
  list("2003 - 2008" = era1, "2009 - 2013" = era2, "2014 - 2018" = era3),
  add_reference_rows = T, exponentiate = T, type = "faceted", colour = F
)
```

>>>>

```{r results='asis'}
f_vx770 <- update(f, . ~ . + A_Vx770)
vx770_cox_res <- coxph(f_vx770,
  data = annual[annual$ReviewYear >= 2011, ],
  cluster = eDWID
)
t1 <- vx770_cox_res %>%
  tbl_regression(exponentiate = T)
t1
ggcoef_table(vx770_cox_res,
  show_p_values = F, add_reference_rows = T, exponentiate = T,
  signif_stars = F, colour = F
)
```

@@

```{r}
f_vx809comb <- update(f, . ~ . + A_VX809comb)
vx809comb_cox_res <- coxph(f_vx809comb,
  data = annual[annual$ReviewYear >= 2015, ],
  cluster = eDWID
)
t2 <- vx809comb_cox_res %>%
  tbl_regression(exponentiate = T)
t2
ggcoef_table(vx809comb_cox_res,
  show_p_values = F, add_reference_rows = T, exponentiate = T,
  signif_stars = F, colour = F
)
```

### Combined results

```{r}
tbl_merge(
  tbls = list(t1, t2),
  tab_spanner = c("VX770", "VX809comb")
)
comb_plot = ggcoef_compare(
  list("VX770" = vx770_cox_res, "VX809comb" = vx809comb_cox_res),
  add_reference_rows = T, exponentiate = T, type = "faceted", colour = F
)
comb_plot
ggsave("./Dissemination/Figures/vx_combined_forest.png",
  plot = comb_plot, width = 12, height = 9, units = "in"
)
```

@@

```{r}
tbl_merge(
  tbls = list(t1, t2, t3),
  tab_spanner = c("2003 - 2008", "2009 - 2013", "2014 - 2018")
)
comb_plot = ggcoef_compare(
  list("2003 - 2008" = era1, "2009 - 2013" = era2, "2014 - 2018" = era3),
  add_reference_rows = T, exponentiate = T, type = "faceted", colour = F
)
comb_plot
ggsave("./Dissemination/Figures/time_combined_forest.png",
  plot = comb_plot, width = 12, height = 9, units = "in"
)
```
